Matching bullets

### 2015-11-23 imaging-paper.Rnw
Fix image to use only a single x value

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2.5, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

qplot(data=subset(dbr111, x <= 100*1.5625^2 & x >= 95*1.5625^2), y, value, colour=factor(x), geom="line", size=I(1)) +
  geom_line(aes(x=xpred, y=ypred, group=x), 
            colour="grey30", size=0.25) +
  scale_colour_brewer("Cross-sections at x", palette="Paired") + 
  ylab(expression(paste("Surface Measurements (in ",mu,m,")", sep=""))) + 
  theme_bw() + 
  theme(legend.position="bottom") + coord_equal()
@

>>>>

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2.5, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across a fixed x value. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

qplot(data=subset(dbr111, x <= 100*1.5625^2 & x >= 99*1.5625^2), y, value, geom="line", size=I(1)) +
  geom_line(aes(x=xpred, y=ypred, group=x), 
            colour="grey30", size=0.25) +
  ylab(expression(paste("Surface Measurements (in ",mu,m,")", sep=""))) + 
  theme_bw() + 
  theme(legend.position="bottom") + coord_equal()
@
